Dynamic Knapsack Problem

### 2021-04-03 Manuscript/Manuscript.tex
initial implementation done
- but I am sure there are bugs, as it is unable to even find an initial feasible solution

	\item $\beta^{ps}$ constraints
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - \sum_{t} sc_{t+1m-1dc} \\ 
				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
	\end{multline}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - \sum_{t} sc_{t+1mdc} \\ 
				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
	\end{equation}

>>>>

	\item $\beta^{ps}$ constraints
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tmdc} - 
				\gamma \Big( ps_{t+1m-1dc}(1-pwp) + ps_{t+1m-1d-1c} pwp - sc_{t+1m-1dc} \\ 
				 - \sum_{t'} rsc_{t+1t'm-1dc} + \sum_{t} rsc_{tt'+1m-1dc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} m \in \{1 ... M-1 \} dc
	\end{multline}
	\begin{multline}
		\sum_{\vec{S}\vec{A}}w \bigg( ps_{tMdc} - 
				\gamma \sum_{M-1}^{M} \Big( ps_{t+1mdc}(1-pwp) + ps_{t+1md-1c} pwp - sc_{t+1mdc} \\ 
				 - \sum_{t'} rsc_{t+1t'mdc} + \sum_{t} rsc_{tt'+1mdc} \Big) \bigg) \\ 
				 \ge E[ps_{tmdc}] \quad \forall t \in \{t...T-1 \} dc
	\end{multline}
	\begin{equation}
		\sum_{\vec{S}\vec{A}} \vec{w} (ps_{Tmdc}) \ge E[ps_{Tmdc}] \quad \forall mdc
	\end{equation}
